The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-07 draft/ms.tex
Title changed
section 2.9 done and half of 2.10, need to start from SHK

\title{Updates on the Exoplanet Orbit Database}

@@

@@

ZZZ For KOIs without MSINI measured, we calculate their mass using the
mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use
\cite{Lissauer2011}, and for KOIs with $6\rearth<R<17\rearth$ we use
\cite{Mordasini2012}.

@@

@@

%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}

@@

@@

@@

We also report the upper limits for planet mass (MSINI), eccentricity
(ECC), and the velocity semi-amplitude (K) when the literatures only
provide the upper limits and not the actual values. The upper limits
for ECC is reported when the orbit is circular, and the upper limits
for K is reported when there is no radial velocity detection. If only
upper limits are given, we set the field to 0, the uncertainty to half
of the upper limit, and the upper limits to the upper limits. For
example, if the literature reports the upper limit for ECC, then we
put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC
to ECCUL/2.

@@

Added field: MONTH, PLANETDISCMETH, STARDISCMETH.
The following fields now have XREF and XURL: (previously in
\cite{Wright2011}) DIST, TRANSIT, BINARY; (new) fields in stellar
parameters: V, VSINI, GAMMA; all orbit pars except for trend and
freeze\_ecc; all transit parameters; all SE parameters; fields for
stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.

VREF is not the same as REF for J H KS, which do not have XREF
fields. See \cite{Wright2011} for references of J H KS mags -- I think
he mentioned it there.

Other general reference fields: In \cite{Wright2011}: FIRSTREF,
FIRSTURL, ORBREF, ORBURL. New: SPECREF, SPECURL contain source of most
of the spectroscopic parameters listed for convenience; actual
references in the REF fields take precedence over this one.

{\bf MONTH} field reports the month in integer when the
peer-reviewed paper is accepted to the ApJ to better track of the
trend in the exoplanet detections.

{\bf PLANETDISCMENT} and {\bf STARDISCMETH} are the fields that report
the discovery methods for the host star and the planet See Section~
for more details.

%------------------------------------------------------------------------------
\subsection{Revised and Removed Fields}
ZZZ CPSNAME?

@@

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by ZZZ Rossiter-McLaughlin
effect. $\lambda$ is introduced because the true spin-orbit angle
($\phi$), defined as the angle between the stellar spin axis and the
orbital axis, is normally not directly measurable. We follow the
definition of $\lambda$ in Fabrycky and Winn 2009 where the
coordinates are defined as follows; the $z$-axis points toward the
observer, the $x$-axis points along the intersection of the sky plane
and the planet's orbital plane with the ascending node of the planet
having $x<0$, and the $y$-axis completes a right
handed-triad. $\lambda$ is measured clockwise on the sky from the
$y$-axis to the projected stellar rotational axis. Some literatures
report $\beta = -\lambda$ instead. We sorted these cases out and made
sure that our $\lambda$'s are following the definition of Fabrycky and
Winn 2009.

{\bf I} is the orbital inclination. This field is not newly added but
we chose to describe it here since our database now has the
inclination for planets detected by methods other than
transit. Previously, only transiting systems used to have the
inclination measured. However, now sometimes for non-transiting
systems the values of I are also available. For instance, if the
system was first detected by radial velocity and has a follow-up
transit observation, then the inclination can be measured. To sum up,
all the transiting planets have measured orbital inclination and
currently, we also have one microlensing planet with measured
inclination. *** give the example!

{\bf OTHERNAME} - This is now listed as other name of planet instead
of star; ** OTHTERNAME has always been the name of the star I
think...?

{\bf DISCMETH} field previously reported the mouthed of discovery,
which was either radial velocity or transit. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and {\bf STARDISCMETH} to better report how
the host star and the planet are detected. Furthermore, they now have
value of one of the following: radial velocity, transit, imaging,
microlensing, timing, or astrometry.

{\bf S} field previously reported the Mount Wilson Ca II S-value and
now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
field, and it is unreferenced at the moment though we plan to include
proper reference in the future.

@@

OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata & \ref{sec:disc} \\

@@

SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata & \ref{sec:stellarmag} \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata & W11 \\

>>>>

\title{The Exoplanet Orbit Database 2, 2014 updates}

@@

{\bf DISCMETH} field previously reported the method of discovery,
which was either radial velocity or transit. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better report how
the host star and the planet are detected. PLANETDISCMETH and STARDISCMETH are the fields that report the discovery methods for the planet and the first planet around the host star, respectively. Furthermore, they now have values of one of the following: radial velocity, transit, imaging,
microlensing, timing, or astrometry.

{\bf MONTH} field reports the month in integer when the
peer-reviewed paper is accepted to the ApJ.

@@

For KOIs without MSINI measured, we calculate their mass using the
mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use
\cite{Lissauer2011}, and for KOIs with $6\rearth<R<11.7\rearth$ we use
\cite{Mordasini2012}.

@@

{\bf I} is the orbital inclination. Previously, only transiting systems have I measured but now, sometimes, non-transiting systems have I's reported too. ZZZ(add reference) For example, one microlensing system has I measured (OGLE-2006-BLG-109L).

@@

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by, e.g., the Rossiter-McLaughlin
effect or planet transiting star spots ZZZ add references for RM effect and the star spot method. $\lambda$ is introduced because the true spin-orbit angle
($\phi$), defined as the angle between the stellar spin axis and the
orbital axis, is normally not directly measurable. We follow the
definition of $\lambda$ in \cite{Fabrycky2009} where the
coordinates are defined as follows; the $z$-axis points toward the
observer, the $x$-axis points along the intersection of the sky plane
and the planet's orbital plane with the ascending node of the planet
having $x<0$, and the $y$-axis completes a right
handed-triad. $\lambda$ is measured clockwise on the sky from the
$y$-axis to the projected stellar rotational axis. $\lambda$ is not a newly added field but we describe it here because $\lambda$'s were not reported consistently since some literatures
report $\beta = -\lambda$ instead. We sorted these cases out and made
sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.
%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}

@@

{\bf SHK} is the Mount Wilson Ca II S-value and {\bf RHK} is the Chromospheric activity of star as $\log{R'_{HK}}$
: field previously reported the  and
now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
field, and it is unreferenced at the moment though we plan to include
proper reference in the future.

@@

We naively propagate the error in PAR to DIST.

@@

We also report the upper limits (XUL) for planet mass (MSINI), eccentricity (ECC), and the velocity semi-amplitude (K) when the literatures report them. For example, the upper limits for ECC is reported when the orbit is circular, and the upper limits for K is reported when there is no radial velocity detection. If only
upper limits are given, we set the field to 0, the uncertainty to half
of the upper limit, and the upper limits to the upper limits. For
example, if the literature reports the upper limit for ECC, then we
put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC
to ECCUL/2. Since not all authors define the upper limits in the same way (e.g. 1$\sigma$ or some fixed percentile), we encourage the readers to refer to the literature for more information.

@@

Previously, we only reported general references (e.g. FIRSTREF, FIRSTURL, ORBREF, and ORBURL), but now we report the references for most of the fields.

ZZZ RA, DEC, and PAR do not have references but they are from the \textit{Hipparcos} by \cite{van Leeuwen2009}. $B-V$ (BMV) field does not have a reference but the values are from the \textit{Hipparcos} catalog. The fields J H and KS do not have references as well but they are from the 2MASS \citep{Skrutskie2006}. The KP field do not have reference but the values are from the Exoplanet Archive \citep{Akeson2013}.

%------------------------------------------------------------------------------
\subsection{Revised and Removed Fields}

@@

@@

OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of star & \nodata & \ref{sec:disc} \\

@@

SHK\dotfill & Float & Mount Wilson Ca {\sc{II}} $S$-value & \nodata & \ref{sec:stellarmag} \\
RHK\dotfill & Float & Chromospheric activity of star as $\log{R'_{HK}}$ & \nodata & W11 \\
